---
title: "Riyadh Radhi Association Rules HW8"
author: "Riyadh Radhi"
date: "March 19, 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Association Rules


```{r message=FALSE, warning=FALSE}

rm(list = ls())
library(arules)
library(arulesViz)
library(MASS)
library(dplyr)
```

### 1. Reading Data + Creating Transaction Object

We will first read our data and split them to create a transaction object
```{r}
df <- read.csv("Online Retail.csv")
splitted_df <- split(df[,"Description"],df[,"InvoiceNo"])
transaction <- as(splitted_df, "transactions")
```

Then we check the summary of our transaction

```{r}
summary(transaction)
```


## 2.Creating Rules with Specific Requirement + Sorting Based on Confidence

Now I will use the *apriori* function to create rules based on what needed and at the same time, I will sort
the rules based on the **confidence** value in a **decreasing** manner 

```{r}
rules <- apriori(transaction, parameter = list(minlen =2, maxlen = 5, supp=0.001 , conf=0.7 ))
rules <- sort(rules, decreasing = TRUE, na.last = NA, by = "confidence")
rules
```

### 3.Inspection The First 30 Rules + Explaining rule #1 & #20

```{r}
inspect(rules[1:30])
```

*First Rule*
```{r}
inspect(rules[1])
```
To get the support value manually,we will divide the (count/number of invoices)
**(19/18536 =0.0010250323)** which is the same as the one in the rule,and to get the lift value, we divide that support value by the propability is A and B(lift = support/P(A)*P(B)) 

**Note** : you can find the number of invoices in the transaction list as number of elements

*Rule Twenty*

```{r}
inspect(rules[20])
```

To get the support value manually,we will divide the (count/number of invoices)
**(22/18536 =0.00118687)** which is the same as the one in the rule, and to get the lift value, we divide that support value by the propability is A and B(lift = support/P(A)*P(B)) 

### 4. Calculating Lift Value

```{r}
d <- subset(rules, subset = lhs %ain% c("REGENCY TEA PLATE GREEN","REGENCY CAKE FORK") & rhs %in% "REGENCY TEA PLATE ROSES")
inspect(d[1])
```

As we can see lift increased to **56.5122**


### 5. Creating a Graph Object for the First Twenty Rules

```{r}
plot(rules[1:20],method= "graph")
```

So what we see in the graph are our **first 20 rules**. They have different sizes based on the support value
starting from the smallest with *0.001* support ending with the largest size with *0.002*. Our color intensity 
tells us about the lift value, the more intense the color, the higher our lift value is. 

Also the graph actually shows the rules based on our description, so we can conclude the if/statement of 
our rules by looking the arrows of each rule and wheather the arrow is outward or inward and so on. 

###(THIS IS EXTRA) I will plot the first five method just to have clear graph because the previews graph is overwhelming.

```{r}
plot(rules[1:5],method= "graph")
```

### 6.What Customers Had Purchased before Buying **REGENCY CAKE FORK**

Please note I'm returning only the lhs of my subset because we are interested in before **REGNCY CAKE FORK** product

```{r}
s <- subset(rules, subset = rhs %in% "REGENCY CAKE FORK")
inspect(unique(s@lhs))
```


### 7. What Products Were Purchased after/along With **REGENCY CAKE FORK**


Plese note that I will use unique with inspect to get only the unique products without repetitives
or unnessceray information

```{r}
f <- subset(rules, subset = lhs %in% "REGENCY CAKE FORK")
inspect(c(unique(f@lhs),unique(f@rhs)))
```

